Untwisting the Boerdijk-Coxeter Helix

### 2017-06-17 doc/TetrahelixUntwist.tex
update

%% TODO: Add something about Tetrobots into abstract.
\begin{abstract}
  The Boerdijk-Coxeter helix (BC helix, or tetrahelix) is a
  face-to-face stack of regular tetrahedra forming a helical column.  Considering the edges of
  these tetrahedra as structural members, the resulting structure is attractive and
  inherently rigid, and therefore interesting to architects,
  mechanical engineers, and roboticists.  A formula is developed that matches the
  visually apparent helices forming the outer rails of the BC helix.
  This formula is generalized to a formula convenient to designers.
  Formulae for 
  computing the
  parameters that give edge-length minimax-optimal tetrahelices
  are given, defining a continuum of optimum tetrahelices of varying curvature.
  The endpoints of this continuum are the BC helix and
  a structure of zero curvature, the \emph{equitetrabeam}.
  Numerically finding the rail angle from the equation for
  pitch allows optimal tetrahelices of any pitch to be designed. 
  An interactive tool for such design and experimentation is provided: \url{https://pubinv.github.io/tetrahelix/}.
  A formula for the inradius of optimal tetrahelices is given.
  The continuum allows a regular Tetrobot in the BC configuration to untwist into a hexapodal or $n$-podal robot
  to use standard gaits.
\end{abstract}

@@

The BC Helix is the end point of a continuum of tetrahelices, the
other end point being an untwisted tetrahelix with equilateral cross
section, constructed by changing the length of only those members
crossing the outside rails after hopping over the nearest
vertex. Under the condition of minimum maximum length ratios of
all members in the system, all such tetrahelices have vertices evenly
spaced along the axis generated by a simple equation and are in fact triple helices.
A machine, such as a robot or a variable-geometry truss, that can change
the length of its members can thus twist and untwist itself by
changing the length of the appropriate members to achieve any point in
the continuum. With a numeric solution, a designer may choose
a rotation angle and member lengths to obtain a desired pitch.

@@

\bibliographystyle{siamplain}
\bibliography{IEEEabrv,gluss}

>>>>

%% TODO: Add something about Tetrobots into abstract.
\begin{abstract}
  The Boerdijk-Coxeter helix (BC helix, or tetrahelix) is a
  face-to-face stack of regular tetrahedra forming a helical column.  Considering the edges of
  these tetrahedra as structural members, the resulting structure is attractive and
  inherently rigid, and therefore interesting to architects,
  mechanical engineers, and roboticists.  A formula is developed that matches the
  visually apparent helices forming the outer rails of the BC helix.
  This formula is generalized to a formula convenient to designers.
  Formulae for 
  computing the
  parameters that give proven edge-length minimax-optimal tetrahelices
  are given, defining a continuum of optimum tetrahelices of varying curvature.
  Only $1/3$rd of the members in the system change their length to reach
  any point in the continuu.
  The endpoints of this continuum are the BC helix and
  a structure of zero curvature, the \emph{equitetrabeam}.
  Numerically finding the rail angle from the equation for
  pitch allows optimal tetrahelices of any pitch to be designed. 
  An interactive tool for such design and experimentation is provided: \url{https://pubinv.github.io/tetrahelix/}.
  A formula for the inradius of optimal tetrahelices is given.
  The continuum allows a regular Tetrobot supporting a length change of less than $16\%$ in the
  BC configuration to untwist into a hexapodal or $n$-podal robot
  to use standard gaits.
\end{abstract}

@@

There exists a continuum of minimax edge-length optimal tetrahelices
having as one end-poing the Boerdijk-Coxeter Helix and at  the
other end point a completely untwisted tetrahelix with equilateral cross
section and planar faces, the equitetrabeam.
By changing the length of only $1/3$ of
the members by less than $16\%$, all configurations in the continuum may be reached.
All such optimal tetrahelices have vertices evenly
spaced along the axis generated by a simple equation and are in fact triple helices.
A machine, such as a robot or a variable-geometry truss, that can change
the length of its members by $16\%$ can thus twist and untwist itself.
A completely regular Tetrobot can thus untwist itself to create a planar
face on the ground for locomotion.
With a numeric solution, a designer may choose
a rotation angle and member lengths to obtain an optimal tetrahelix design
of any pitch.

@@

\bibliographystyle{asmems4}
\bibliography{IEEEabrv,gluss}
